Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
Refactored: \subsubsection{Question 1: Heterogenous Data Tasks}

\begin{abstract}
%% While people often draw upon diverse sources of information in the course of common tasks, tool support for integrating information from diverse information sources remains scarce. This paper presents an exploratory, sequential mixed-method study of user-driven data integration methods for PIM tools...
%% exploratory, sequential mixed-method study of 
\end{abstract}

@@

\subsubsection{Results - Heterogeneous Data Tasks}
The participants, recruited informally via word of mouth, consisted of 7 male and 1 female. They were split evenly into two age groups of 18-25 and 26-32.   
% mention # that were computer scientists here?

% not so relevant:
% All but one participant reported they used social network sites very regularly (many times a day); they said they either logged in multiple times a day, left a website page open or used dedicated application for their social networking site updates.  Those that used social networking websites primarily used Facebook.  All of the participants used Twitter to listen to broadcasted tweets, and 6 out of 8 people regularly tweeted.  The following two sections, describe the tasks people perform online with heterogeneous data and how they would use to organise a large social event.
% \subsubsection{Question 1: Heterogenous Data Tasks}
All participants regularly using multiple websites to accomplish tasks.  Example of such tasks included shopping (including food, consumer electronics, hotels and flights), choosing restaurants, searching for jobs, selecting a university, seeking recipes, and finding answers to technical problems.  The biggest focus for shopping focused tasks was balancing price, quality and speed of delivery.  In general, people did not not trust single websites for reviews because they said that they could be biased and did not always review the features they were interested in.  One participant said that video reviews of items were really important because they showed the aesthetics and scale of the item.  In general, for initial research into organising a task, it was typical to use Google to search for several related websites.  They identified that they used different websites for different jobs, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.  Social networks were also identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.

@@

\subsection{Does DataPalette facilitate serendipitous data integration?}

We set out to test three hypotheses with the DataPalette study. The first was that end-user citizens would understand the interface mechanisms of DP (h1).  The second, h2, was that DP enables people to mix and integrate heterogeneous data in the process of performing their tasks.  The third, h3, was that using DP facilitatedp task completion (h3).  Using real data obtained from typical data sources identified during our prestudy (PS.1), we tested the DP prototype and its integration interaction mechanisms with ``real'' users, who were students, staff and alumni of our University who had varying backgrounds and levels of expertise with computers.

>>>>

\begin{abstract}
%% While people often draw upon diverse sources of information in the course of common tasks, tool support for integrating information from diverse information sources remains scarce. This paper presents an exploratory, sequential mixed-method study of user-driven data integration methods for PIM tools...

exploratory, sequential mixed-method study of 
\end{abstract}

@@

\subsubsection{Results - Heterogeneous Data Tasks}

The participants, recruited informally via word of mouth, consisted of 7 male and 1 female. They were split evenly into two age groups of 18-25 and 26-32.   
% mention # that were computer scientists here?

\subsubsection{Question 1: Heterogenous Data Tasks}

All participants reported regular use of multiple websites to accomplish tasks, examples of which including: shopping (including food, consumer electronics, hotels and flights), choosing restaurants, job-seeking, selecting a university, seeking recipes, and finding answers to technical problems.  When beginning a task, it was common for participants to use Google to discover several related websites, which would then be used in different ways depending on the task at hand. For shopping-oriented tasks, balancing price, quality and speed of delivery was the main aim.  For product reviews, single sources were not trusted due to possible bias and incomplete feature coverage.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To provide a full coverage of information, websites of different types were used, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.

@@

\subsection{Revisiting the hypotheses: Does DataPalette facilitate serendipitous data integration?}

We set out to answer three different questions with the DataPalette study. The first concerned whether people understood and could use the system (h1), whether the system enabled people to mix and integrate heterogeneous data (h2), and whether the interface facilitated task completion (h3).  Using real data obtained from typical data sources identified during our prestudy (PS.1), we tested the DP prototype and its integration interaction mechanisms with ``real'' users, who were students, staff and alumni of our University who had varying backgrounds and levels of expertise with computers.
